---
title: "Riverside time studay"
output: html_notebook
---

This workbook is a study of using [lubridate](https://lubridate.tidyverse.org/) to count testing cases by week. My initial testing based on a chapter from [R for Data Science](https://r4ds.had.co.nz/dates-and-times.html) had the counts by week ending on Sunday when I thought that was the beginning of the week. I think this is something about the ceiling_date. I was able to subtract 1 from that ceiling to give me the Saturday date. This checks that logic to make sure I'm not counting the wrong days.

This is the way to formulate the count by week:

`count(week = ceiling_date(lab_date, "week") - 1)`

```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
library(lubridate)
```


## Import cleaned data

```{r}
riverside <- read_rds("data-processed/riverside.rds")
```


```{r}
riverside %>% glimpse()
```

Building test data for feb 2020

```{r}
test_feb <- riverside %>% 
  filter(month(lab_date) == 2)
```

View of Feb data

```{r}
test_feb
```

This shows counts by data at the beginning of the week.

```{r}
test_feb %>% 
  count(week = floor_date(lab_date, "week"))
```

This shows the date of the end of the week. The `ceiling_date` for week is the Sunday of the next week, so I'm substracting one day to get the Saturday. At least that is how it is working for Feb.

```{r}
test_feb %>% 
  count(week = ceiling_date(lab_date, "week")-1)
```

## March test

```{r}
test_mar_ps <- riverside %>% 
  filter(
    lab_date >= "2020-03-1",
    lab_date <= "2020-03-15",
    place == "PALM SPRINGS"
  )
```

```{r}
test_mar_ps
```


```{r}
test_mar_ps %>% 
  count(week = ceiling_date(lab_date, "week")-1)

```

tests the week enxing March 14.

```{r}
test_mar_ps %>% 
  filter(
    lab_date >= "2020-03-08",
    lab_date <= "2020-03-14"
  )
```

